---
title: "Data Science in Healthcare"
author: "Natalie Borter, Pascal Humbel, Jonathan Hahn"
date: "18.01.2021"
output: html_document;
        pdf_document
params:
  wd: !r getwd()
---

```{r setup, include=True, cache=TRUE}
# Setting working directory to the directory of the file
knitr::opts_knit$set(root.dir = getwd())
source("collecting_data.R")
## executing data preparation with function load_dada_frame() defined in collecting_data.R

# Natalie & hits

# define the keywords for google trend analysis
keyword.vec<-c("Joghurt", "Abnehmen")

# union of all yogurts
df<-load.data.frame(keyword.vec)

# list of all yogurts 
dfs<-load.data.frames(keyword.vec)

dfs
```

###Describe the dependent variable: waiting times and some of the key predictors


```{r boxplots, warning=FALSE, message=FALSE}
ggplot(df, aes(x=yrwk_start, y=sales)) + 
    geom_line(aes(colour=article_name, group=article_name)) + # colour, group both depend on cond2
    geom_point(aes(colour=article_name),               # colour depends on cond2
               size=1)                          # larger points, different shape

```
### Prepare the data for analysis

```{r prepare_data, warning=FALSE, message=FALSE}
library(tidyverse)
df_final<-dfs[[1]]


# TODO: load swiss hollydays
# Holydays for Prophet

#hG_factoreneva <- read.csv2(file = 'Data/fcal_Geneve_2019.csv', sep = ';')
#hG_factoreneva[,"Date"]<-as.Date(hG_factoreneva$Datum,format="%d.%m.%Y" )
#hG_factoreneva$Wochentag<-NULL
#hG_factoreneva$Kalenderwoche<-NULL
#hG_factoreneva$X<-NULL
#hG_factoreneva$Datum<-NULL

# create lockdown
ld_start = as.Date("08.04.2020", format="%d.%m.%Y")
ld_end = as.Date("26.04.2020", format="%d.%m.%Y")
ld<-data.frame("Date" = seq(ld_start,ld_end, by = 'days'), row.names = )
ld[,"Bezeichnung"]<-"Lockdown"

#events<-rbind(ld, hG_factoreneva)
events <- ld

h<-data_frame(
  holiday = events[,"Bezeichnung"],
  ds = as.Date(events[,"Date"]),
  lower_window = 0,
  upper_window = 1
)

# refactor columns for prophet package
A<-df_final[,c("yrwk_start", "sales")]
names(A)<-c("ds","y")
```

### Compare different models
For comparison of the models
https://www.otexts.org/fpp/2/5


```{r rmse_function}
##define two functions to assess model fit

## rmse = root mean squared error
rmse<-function(actual, predicted){
  round((sum((actual-predicted)^2)/length(actual))^.5,2)
}
## mean absolute percentage error
mape<-function(actual, predicted){
  round(mean(100*abs((actual-predicted)/actual)),2)
}
```

Partition the data into train and test
```{r prepare_data_for_prophet}
AL<-df_final[,c("yrwk_start", 
                "sales",
                "year", 
                "month", 
                "week", 
                "promo_01", 
                "promo_02", 
                "promo_03", 
                "promo_04", 
                "promo_05",
                "Joghurt",
                "Abnehmen")]
names(AL)<-c("ds",
             "y",
             "year",
             "month",
             "week",
             "promo_01",
             "promo_02",
             "promo_03",
             "promo_04",
             "promo_05",
             "Joghurt",
             "Abnehmen")

## the test set is the last 4 weeks measured, the training set is everithing else
ntest <- 12 # measurements weeks
len <- nrow(AL)
training<-AL[1:(len-ntest),]
testing<-AL[(len-ntest+1):len,]

c(min(training$ds), max(training$ds))
c(min(testing$ds), max(testing$ds))
```

## Median: as more as 50% of the waiting times are 5 minutes (Median), a model predicting always the median is used for comparison
```{r fitting_mean, warning=FALSE, message=FALSE}

training$pred_median <-median(training$y)
testing$pred_median <-median(training$y)


c(rmse(training$y, training$pred_median),rmse(testing$y, testing$pred_median))
c(mape(training$y, training$pred_median),mape(testing$y, testing$pred_median))
```



## GAM: As second model to compare with, a generalized additive model with smoothness estimation is used (GAM). 
```{r fitting_gam, warning=FALSE, message=FALSE}
library(gam)

fit_gam<-gam(y~ds+ 
               week + 
               month +
               year +
               promo_01+
#               promo_02+
               promo_03+
               promo_04+
#               promo_05
               Joghurt+
               Abnehmen
             ,data=training)

training$pred_gam <-predict(fit_gam)
testing$pred_gam <-predict(fit_gam, newdata = testing)

c(rmse(training$y, training$pred_gam),rmse(testing$y, testing$pred_gam))
c(mape(training$y, training$pred_gam),mape(testing$y, testing$pred_gam))
```


## Prophet: As third model prophet ist used, first only with holidays added
```{r install_library, warning=FALSE, message=FALSE}
library(prophet)
```
```{r prophet_with_holyday_model, cache=TRUE}
m <- prophet(holidays=h, mcmc_samples=300, 
             holidays_prior_scale=0.5, 
             changepoint_prior_scale=0.01, 
             yearly.seasonality=TRUE,
             weekly.seasonality=TRUE, 
             daily.seasonality=TRUE)
m <- add_country_holidays(m, country_name = 'CH')
m <- fit.prophet(m, training)
```

Do a forecast for the model with holidays
```{r prophet_with_holydays_prediction, cache=TRUE}

future <- make_future_dataframe(m, periods = ntest, freq = 60 *60, include_history = TRUE)

fcst <- predict(m, future)
```

First visual inspection
```{r prophet_with_holydays_visual, cache=TRUE}
plot(m, fcst) + add_changepoints_to_plot(m)
prophet_plot_components(m,fcst)
```

Check the accuracy of the models
```{r prophet_with_holydays_prediction_accuracy}
n<-nrow(training)

training$yhat<-fcst$yhat[1:n]
testing$yhat<-fcst$yhat[(n+1):(n+ntest)]

c(rmse(training$y, training$yhat),rmse(testing$y, testing$yhat))
c(mape(training$y, training$yhat),mape(testing$y, testing$yhat))
```


### Second Prophet Model, this time with both, regressors and holidays


```{r prophet_with_holydays_model, cache=TRUE}
m_h_r <- prophet(holidays=h, mcmc_samples=300, 
             holidays_prior_scale=0.5, 
             changepoint_prior_scale=0.01, 
             #seasonality_mode='multiplicative', 
             yearly.seasonality=TRUE, 
             weekly.seasonality=TRUE, 
             daily.seasonality=FALSE)


m_h_r <- add_regressor(m_h_r, 'promo_01')
m_h_r <- add_regressor(m_h_r, "promo_02")
m_h_r <- add_regressor(m_h_r, 'promo_03')
m_h_r <- add_regressor(m_h_r, "promo_04")
m_h_r <- add_regressor(m_h_r, 'promo_05')
m_h_r <- add_regressor(m_h_r, "Joghurt")
m_h_r <- add_regressor(m_h_r, "Abnehmen")
m_h_r <- fit.prophet(m_h_r, training)
```

do a forecast for the model with holydays and regressors
```{r prophet_with_holydays_and_regressors_prediction, cache=TRUE}
future <- make_future_dataframe(m_h_r, periods = ntest, freq = 60 *60, include_history = TRUE)

future$promo_01<- AL[,c("promo_01")]
future$promo_02<- AL[,c("promo_02")]
future$promo_03<- AL[,c("promo_03")]
future$promo_04<- AL[,c("promo_04")]
future$promo_05<- AL[,c("promo_05")]
future$Joghurt<- AL[,c("Joghurt")]
future$Abnehmen<- AL[,c("Abnehmen")]

fcst_h_r <- predict(m_h_r, future)
```

First visual inspection
```{r prophet_with_holydays_and_regressors_visual}
plot(m_h_r, fcst_h_r) + add_changepoints_to_plot(m_h_r)
p <- prophet_plot_components(m_h_r,fcst_h_r, render_plot = TRUE)
```

Check the accuracy of the model
```{r prophet_with_holydays_and_regressors_prediction_accuracy}
n<-nrow(training)

training$yhat_h_r<-fcst_h_r$yhat[1:n]
testing$yhat_h_r<-fcst_h_r$yhat[(n+1):(n+ntest)]

a<-training$yhat_h_r<5
training$yhat_h_r[a]<-5

b<-testing$yhat_h_r<5
testing$yhat_h_r[b]<-5

c(rmse(training$y, training$yhat_h_r),rmse(testing$y, testing$yhat_h_r))
c(mape(training$y, training$yhat_h_r),mape(testing$y, testing$yhat_h_r))
```
```{r rename_predictions_for_plot}
training<-training %>% rename(pred_prophet = yhat, pred_prophet_regressors = yhat_h_r )
testing<-testing %>% rename(pred_prophet = yhat, pred_prophet_regressors = yhat_h_r )
```
Plot the four models against eachother and add RMSE and MAPE
```{r plot_and_compare_models, warning=FALSE ,message=FALSE}
testqstat<- data.table::melt(testing, id="ds", measure=c("pred_prophet", 
                                                         "pred_prophet_regressors", 
                                                         "pred_gam", 
                                                         "pred_median"))

model_names<- c(
  'pred_prophet' = sprintf("Prophet Holydays \n RMSE: %.2f (Train) - %.2f (Test)",
                   rmse(training$y, training$pred_prophet),rmse(testing$y, testing$pred_prophet)),
  
  'pred_prophet_regressors' = sprintf(
    "Prophet with Regressors \n RMSE: %.2f (Train) - %.2f (Test)",
                   rmse(training$y, training$pred_prophet_regressors),
                    rmse(testing$y, testing$pred_prophet_regressors)),
  
  'pred_gam' = sprintf("GAM \n  RMSE: %.2f (Train) - %.2f (Test)",
                   rmse(training$y, training$pred_gam),rmse(testing$y, testing$pred_gam)),  
  
  'pred_median' = sprintf("Median \n RMSE: %.2f (Train) - %.2f (Test)",
                   rmse(training$y, training$pred_median),rmse(testing$y, testing$pred_median))
)


g1 <- ggplot(aes(y=value, x=ds, color=variable), data=testqstat) +
  
  xlim(min(testing$ds), max(testing$ds))+
  geom_line(data = testing, aes(y=y), color="grey70") +
  geom_line() +
  facet_wrap(~variable, ncol=2, labeller = as_labeller(model_names))+
  theme(axis.text = element_text(size=5), axis.title = element_text(size=6)) +
  labs(title="Modelcomparison, Test Data, with rmse and mape Statistics.", 
       x="Time", y="WaitingTime in min")+ 
  theme(legend.position = "none")
g1
```