---
title: "Predicting MIGROS Yogurt Sales"
author: "Natalie Borter, Beatrice Stierli, Sinah Schüpfer, Adrian Peng, Loris Lindemann, Raphael Suter, Jonathan Hahn"
date: "20.10.2021"
output: html_document;
        pdf_document
params:
  wd: !r getwd()
---

```{r setup, include=TRUE, cache=TRUE, results = 'hide', warning=FALSE, message=FALSE}
# Setting working directory to the directory of the file
knitr::opts_knit$set(root.dir = getwd())
source("collecting_data.R")

set.seed(123)

# define the keywords for google trend analysis
keyword.vec<-c("Joghurt", "gesund essen")

data.folder <-("data_hs21") 
# list of all yogurts with own data frame for each yogurt
dfs<-load.data.frames(keyword.vec, data.folder)

```

## Describe the dependent variable: waiting times and some of the key predictors

```{r rmse_mape, warning=FALSE, message=FALSE}

## define two functions to assess model fit

## rmse = root mean squared error
rmse<-function(actual, predicted){
  round((sum((actual-predicted)^2)/length(actual))^.5,2)
}
## mean absolute percentage error
mape<-function(actual, predicted){
  round(mean(100*abs((actual-predicted)/actual)),2)
}

```

### Prediction of unknown Regressors

* milk prices
* yogurt prices
* google trends


```{r predict_regressors, warning=FALSE, message=FALSE}
library(forecast)

gesund<-dfs[[1]]$gesund.essen
Joghurt<-dfs[[1]]$Joghurt

joghurt.price<-dfs[[1]]$kon.yougurtpr.180.fru
milk.price<-dfs[[1]]$prod.milchpreis.a

ntest <- 15 # measurements months

len <- length(gesund)
```


### Predict the Google trends value of the key word "gesund essen".

Predict the future google trends value for the keyword "gesund essen" in Switzerland.

```{r predict_gtrends_gesund}
trainingg<-gesund[c(1:(len-ntest))]
testingg<-gesund[c((len-ntest+1):len)]
arima.ges<-auto.arima(trainingg, ic = "aic")
ges.pred <- predict(arima.ges, n.ahead = ntest)
checkresiduals(arima.ges)
```


### Predict the Google trends value of the key word "Joghurt".

Predict the future google trends value for the keyword "Joghurt" in Switzerland.

```{r predict_gtrends_yogurt}
trainingJ<-Joghurt[c(1:(len-ntest))]
testingJ<-Joghurt[c((len-ntest+1):len)]
arima.Jog<-auto.arima(trainingJ, ic = "aic")
Jog.pred <- predict(arima.Jog, n.ahead = ntest)
checkresiduals(arima.Jog)
```


### Predict the yogurt price

Predict the future [yogurt price](https://www.blw.admin.ch/blw/de/home/markt/marktbeobachtung/milch.html#:~:text=Steigender%20Preis%20f%C3%BCr%20Molkereimilch,im%20Vergleich%20zum%20entsprechenden%20Vorjahreszeitraum) in Switzerland.

```{r predict_yogurt_price}
trainingJP<-joghurt.price[c(1:(len-ntest))]
testingJP<-joghurt.price[c((len-ntest+1):len)]
arima.JP<-auto.arima(trainingJP, ic = "aic")
JP.pred <- predict(arima.JP, n.ahead = ntest)
checkresiduals(arima.JP)
```


### Predict the milk price

Predict the future [milk price](https://www.blw.admin.ch/blw/de/home/markt/marktbeobachtung/milch.html#:~:text=Steigender%20Preis%20f%C3%BCr%20Molkereimilch,im%20Vergleich%20zum%20entsprechenden%20Vorjahreszeitraum) in Switzerland.

```{r predict_milk_price}
trainingMP<-milk.price[c(1:(len-ntest))]
testingMP<-milk.price[c((len-ntest+1):len)]
arima.MP<-auto.arima(trainingMP, ic = "aic")
MP.pred <- predict(arima.Jog, n.ahead = ntest)
checkresiduals(arima.MP)
```

Create a series of known values and predicted ones.

```{r create_series_of_prediction}
ts.pred.gesund <- c(trainingg, as.numeric(ges.pred$pred))
ts.pred.joghurt <- c(trainingJ, as.numeric(Jog.pred$pred))
ts.pred.joghurt.price <- c(trainingJP, as.numeric(JP.pred$pred))
ts.pred.milk.price <- c(trainingMP, as.numeric(MP.pred$pred))
```


## Apply each model to each yogurt

A loop that applies each model to each yogurt.
The relevant data is stored for comparison.
```{r prepare_loop, warning=FALSE, message=FALSE, cache=TRUE}
library(party)
library(prophet)
library(tidyverse)
library(xgboost)

## Define data frame for each model

d_lm = data.frame(prod = rep(0,19), 
                  model = rep(0,19), 
                  rmse_t=rep(0,19), 
                  rmse_test=rep(0,19), 
                  mape_t=rep(0,19),
                  mape_test=rep(0,19))

d = data.frame(prod = rep(0,19), 
                  model = rep(0,19), 
                  rmse_t=rep(0,19), 
                  rmse_test=rep(0,19), 
                  mape_t=rep(0,19),
                  mape_test=rep(0,19))

d_glm = data.frame(prod = rep(0,19), 
                  model = rep(0,19), 
                  rmse_t=rep(0,19), 
                  rmse_test=rep(0,19), 
                  mape_t=rep(0,19),
                  mape_test=rep(0,19))

d_prop1 = data.frame(prod = rep(0,19), 
                  model = rep(0,19), 
                  rmse_t=rep(0,19), 
                  rmse_test=rep(0,19), 
                  mape_t=rep(0,19),
                  mape_test=rep(0,19))

d_prop2 = data.frame(prod = rep(0,19), 
                  model = rep(0,19), 
                  rmse_t=rep(0,19), 
                  rmse_test=rep(0,19), 
                  mape_t=rep(0,19),
                  mape_test=rep(0,19))

d_xgboost = data.frame(prod = rep(0,19), 
                  model = rep(0,19), 
                  rmse_t=rep(0,19), 
                  rmse_test=rep(0,19), 
                  mape_t=rep(0,19),
                  mape_test=rep(0,19))

d_factorM = data.frame(prod = rep(0,19), 
                  model = rep(0,19), 
                  rmse_t=rep(0,19), 
                  rmse_test=rep(0,19), 
                  mape_t=rep(0,19),
                  mape_test=rep(0,19))

d_factorR = data.frame(prod = rep(0,19), 
                  model = rep(0,19), 
                  rmse_t=rep(0,19), 
                  rmse_test=rep(0,19), 
                  mape_t=rep(0,19),
                  mape_test=rep(0,19))

prediction <- list()
```

```{r loop_over_models, warning=FALSE, message=FALSE, cache=TRUE,}
## Loop over each yogurt and apply data on each model

for(i in seq(1,length(dfs))){
  
  ## replace Null values
  dfs[[i]][is.na(dfs[[i]])] <- 0
  
  ## add prediction of Gtrends
  dfs[[i]]["pred.joghurt"]<-ts.pred.joghurt
  dfs[[i]]["pred.gesund"]<-ts.pred.gesund
  
  ## add prediction of milk and yogurt prices
  dfs[[i]]["pred.joghurt.price"]<-ts.pred.joghurt.price
  dfs[[i]]["pred.milk.price"]<-ts.pred.milk.price
  
  df_final<-dfs[[i]]

  ## create lockdown
  ld_start = as.Date("08.04.2020", format="%d.%m.%Y")
  ld_end = as.Date("26.04.2020", format="%d.%m.%Y")
  ld<-data.frame("Date" = seq(ld_start,ld_end, by = 'days'), row.names = )
  ld[,"Bezeichnung"]<-"Lockdown"

  #events<-rbind(ld, hG_factoreneva)
  events <- ld

  h<-data_frame(
    holiday = events[,"Bezeichnung"],
    ds = as.Date(events[,"Date"]),
    lower_window = 0,
    upper_window = 1
  )

  ## refactor columns for prophet package
  A<-df_final[,c("yrwk_start", "sales")]
  names(A)<-c("ds","y")

  AL<-df_final[,c("yrwk_start", 
                  "sales",
                  "year", 
                  "month", 
                  "week", 
                  "promo_01", 
                  "promo_02", 
                  "promo_03", 
                  "promo_04", 
                  "promo_05",
                  "pred.joghurt",
                  "pred.gesund",
                  "pred.joghurt.price",
                  "pred.milk.price")]
  
  names(AL)<-c("ds",
               "y",
               "year",
               "month",
               "week",
               "promo_01",
               "promo_02",
               "promo_03",
               "promo_04",
               "promo_05",
               "pred.joghurt",
               "pred.gesund",
               "pred.joghurt.price",
               "pred.milk.price")

  ## the test set is the last 4 weeks measured, 
  ## the training set is everything else
  
  len <- nrow(AL)
  training<-AL[1:(len-ntest),]
  testing<-AL[(len-ntest+1):len,]
  
  ## ------------------------------------------------------------------------
  
  ## Linear Model
  
  mod<-lm(y~ds+
            week+
            month+
            year+
            as.numeric(promo_01)+
            as.numeric(promo_02)
          +as.numeric(promo_03)
          +as.numeric(promo_04)
          +as.numeric(promo_05)
          +pred.joghurt
          +pred.gesund
          +pred.joghurt.price
          +pred.milk.price
          +pred.milk.price, data=training)
  
  testingA<-mod$coefficients[1]+mod$coefficients[2]*as.numeric(testing$week)+mod$coefficients[3]*as.numeric(testing$month)+mod$coefficients[4]*as.numeric(testing$promo_01)
  
  testing$pred_lm <- predict(mod, newdata = testing)
  training$pred_lm <-mod$fitted.values
  
  prod <- df_final$article_name[1]
  model <- "lin1"
  a <- c(rmse(training$y, training$pred_lm),rmse(testing$y, testing$pred_lm))
  b <- c(mape(training$y, training$pred_lm),mape(testing$y, testing$pred_lm))
  c <- c(prod,model,a,b)
  d_lm[i, ] = c
  
  ## ------------------------------------------------------------------------
  
  ## GLM
  
  fit_glm<-glm(y~ds+ 
               week +
               month+
               year+
               as.numeric(promo_01)+
               as.numeric(promo_02)+
               as.numeric(promo_03)+
               as.numeric(promo_04)+
               as.numeric(promo_05)
               #+pred.joghurt
               #+pred.gesund
               #+pred.joghurt.price
               #+pred.milk.price
               ,
               data=training,
               family="quasipoisson")
  summary(fit_glm)
  training$pred_glm <-  exp(predict(fit_glm))
  testing$pred_glm <-  exp(predict(fit_glm, newdata = testing))

  model <- "model_GLM"
  a_glm <- c(rmse(training$y, training$pred_glm),rmse(testing$y, testing$pred_glm))
  b_glm <- c(mape(training$y, training$pred_glm),mape(testing$y, testing$pred_glm))
  c_glm <- c(prod,model,a_glm,b_glm)
  d_glm[i, ] = c_glm
  
  ## ------------------------------------------------------------------------
  
  ## Regression Tree
  
  ## tree with party
  
  tree <- ctree(y~#ds+ #ds taken out -> date is not supported
                  week + 
                  month +
                  year +
                  promo_01+
                  promo_02+
                  promo_03+
                  promo_04+
                  promo_05
                  +pred.joghurt
                  +pred.gesund
                  +pred.joghurt.price
                  +pred.milk.price,
                  data=training)
  
  ## show tree
  #plot(tree)
  
  training$pred_tree <-predict(tree)
  testing$pred_tree <-predict(tree, newdata = testing)
  
  model <- "model_basic_tree"
  a <- c(rmse(training$y, training$pred_tree),rmse(testing$y, testing$pred_tree))
  b <- c(mape(training$y, training$pred_tree),mape(testing$y, testing$pred_tree))
  c <- c(prod,model,a,b)
  d[i, ] = c
  
  ## ------------------------------------------------------------------------
  
  ## Basic Prophet Model
  
  ## specify holidays on weekly basis; 
  ## if holiday in a week the whole week is marked as holiday 
  ## (because data is provided on a weekly basis)
  
  years <- c(2016, 2017, 2018, 2019, 2020, 2021)
  country.name <- 'CH'
  df <- prophet:::make_holidays_df(years, country.name)

  ## make sure that each holiday hots over one week
  df$lower_window<--4
  df$upper_window<-4

  ##combine holidays with the data frame
  df2<-select(df,"holiday","ds","lower_window","upper_window")

  s<-rbind(h,df2)

  m <- prophet(holidays=s, mcmc_samples=300, 
              holidays_prior_scale=0.5, 
               changepoint_prior_scale=0.01, 
              yearly.seasonality=TRUE)
  #m <- add_country_holidays(m, country_name = 'CH')
  #m <- add_country_holidays(m, df)
  m <- fit.prophet(m, training)
  future <- make_future_dataframe(m, periods = ntest, freq = "week", include_history = TRUE)
  fcst <- predict(m, future)
  n<-nrow(training)
  training$pred_prophet1<-fcst$yhat[1:n]
  testing$pred_prophet1<-fcst$yhat[(n+1):(n+ntest)]
  
  model <- "Prophet1"
  a <- c(rmse(training$y, training$pred_prophet1),rmse(testing$y, testing$pred_prophet1))
  b <- c(mape(training$y, training$pred_prophet1),mape(testing$y, testing$pred_prophet1))
  c <- c(prod,model,a,b)
  d_prop1[i, ] = c
  
  ## ------------------------------------------------------------------------
  
  ## Complex Prophet Model (with regressors)
  
  m_h_r <- prophet(holidays=s, mcmc_samples=300, 
             holidays_prior_scale=0.5, 
             changepoint_prior_scale=0.01, 
             #seasonality_mode='multiplicative', 
             yearly.seasonality=TRUE, 
             #weekly.seasonality=TRUE, 
             #daily.seasonality=FALSE
             )
  ## add regressors to the model
  m_h_r <- add_regressor(m_h_r, 'promo_01')
  m_h_r <- add_regressor(m_h_r, "promo_02")
  m_h_r <- add_regressor(m_h_r, 'promo_03')
  m_h_r <- add_regressor(m_h_r, "promo_04")
  m_h_r <- add_regressor(m_h_r, 'promo_05')
  m_h_r <- add_regressor(m_h_r, "pred.joghurt")
  m_h_r <- add_regressor(m_h_r, "pred.gesund")
  m_h_r <- add_regressor(m_h_r, "pred.joghurt.price")
  m_h_r <- add_regressor(m_h_r, "pred.milk.price")
  
  m_h_r <- fit.prophet(m_h_r, training)
  
  ## create the data frame for the prediction
  future <- make_future_dataframe(m_h_r, periods = ntest, freq = "week", include_history = TRUE)

  ## ad actual values to the prediction
  future$promo_01<- AL[,c("promo_01")]
  future$promo_02<- AL[,c("promo_02")]
  future$promo_03<- AL[,c("promo_03")]
  future$promo_04<- AL[,c("promo_04")]
  future$promo_05<- AL[,c("promo_05")]
  future$pred.joghurt<- AL[,c("pred.joghurt")]
  future$pred.gesund<- AL[,c("pred.gesund")]
  future$pred.joghurt.price<- AL[,c("pred.joghurt.price")]
  future$pred.milk.price<- AL[,c("pred.milk.price")]
  
  ## predict
  fcst_h_r <- predict(m_h_r, future)

  n<-nrow(training)

  training$pred_prophet2<-fcst_h_r$yhat[1:n]
  testing$pred_prophet2<-fcst_h_r$yhat[(n+1):(n+ntest)]
  
  model <- "Prophet2"
  a <- c(rmse(training$y, training$pred_prophet2),rmse(testing$y, testing$pred_prophet2))
  b <- c(mape(training$y, training$pred_prophet2),mape(testing$y, testing$pred_prophet2))
  c <- c(prod,model,a,b)
  d_prop2[i, ] = c
  
  ## ------------------------------------------------------------------------
  
  ## XGBOOST
 
  ## We need to provide the x and y variables 
  ## separately and in the following format:
  
  #training
  X <- AL%>%
    select(-y, 
           -ds
           )%>% 
    mutate(across(where(is.factor), as.numeric))%>%
    as.matrix(.)
  
  X_train <- X[1:(len-ntest),]
  
  y <- AL[1:(len-ntest),]%>%
    select(y) %>%
    as.matrix(.)
  
  ## Train model
  fit.gbt <- xgboost(data = X_train, 
                     label = y,
                     nrounds=60, 
                     objective = "count:poisson",
                     verbose = 0)
  
  ## Make predictions on training data
  pred_gbt_train <- predict(fit.gbt, X[1:(len-ntest),])
  ## Make predictions on test data
  pred_gbt_test <- predict(fit.gbt, X[(len-ntest+1):len,])
  
  ## Which variables are important?
  #require(ggplot2)
  #library(Ckmeans.1d.dp)
  #importance=xgb.importance(colnames(X), model = fit.gbt)
  #xgb.ggplot.importance(importance)
  
  training$pred_xgboost<-pred_gbt_train
  testing$pred_xgboost<-pred_gbt_test
  
  c(rmse(training$y, training$pred_xgboost),rmse(testing$y, testing$pred_xgboost))
  c(mape(training$y, training$pred_xgboost),mape(testing$y, testing$pred_xgboost))
  
  model <- "XGBOOST"
  a <- c(rmse(training$y, training$pred_xgboost),rmse(testing$y, testing$pred_xgboost))
  b <- c(mape(training$y, training$pred_xgboost),mape(testing$y, testing$pred_xgboost))
  c <- c(prod,model,a,b)
  d_xgboost[i, ] = c
  
  ## ------------------------------------------------------------------------
  
  ## Prophet with factor scores
  
  ## WHATCH OUT! y is replaced with factor scores to apply the prophet model
  
  AL$y.MCLASSI<-df_final$MClassi
  training$y<-AL$y.MCLASSI[1:(len-ntest)]
  testing$y<-AL$y.MCLASSI[(len-ntest+1):len]

  m_h_r <- prophet(holidays=s, mcmc_samples=300, 
                   holidays_prior_scale=0.5, 
                   changepoint_prior_scale=0.01, 
                   #seasonality_mode='multiplicative', 
                   yearly.seasonality=TRUE, 
                   #weekly.seasonality=TRUE, 
                   #daily.seasonality=FALSE
  )
  
  m_h_r <- add_regressor(m_h_r, 'promo_01')
  m_h_r <- add_regressor(m_h_r, "promo_02")
  m_h_r <- add_regressor(m_h_r, 'promo_03')
  m_h_r <- add_regressor(m_h_r, "promo_04")
  m_h_r <- add_regressor(m_h_r, 'promo_05')
  #m_h_r <- add_regressor(m_h_r, "pred.joghurt")
  #m_h_r <- add_regressor(m_h_r, "pred.gesund")
  #m_h_r <- add_regressor(m_h_r, "pred.joghurt.price")
  #m_h_r <- add_regressor(m_h_r, "pred.milk.price")
  m_h_r <- fit.prophet(m_h_r, training)
  
  future <- make_future_dataframe(m_h_r, periods = ntest, freq = "week", include_history = TRUE)
 
  future$promo_01<- AL[,c("promo_01")]
  future$promo_02<- AL[,c("promo_02")]
  future$promo_03<- AL[,c("promo_03")]
  future$promo_04<- AL[,c("promo_04")]
  future$promo_05<- AL[,c("promo_05")]
  #future$pred.joghurt<- AL[,c("pred.joghurt")]
  #future$pred.gesund<- AL[,c("pred.gesund")]
  #future$pred.joghurt.price<- AL[,c("pred.joghurt.price")]
  #future$pred.milk.price<- AL[,c("pred.milk.price")]
  
  fcst_h_r <- predict(m_h_r, future)
  
  n<-nrow(training)
  
  training$pred_ProphetScoresM<-fcst_h_r$yhat[1:n]
  testing$pred_ProphetScoresM<-fcst_h_r$yhat[(n+1):(n+ntest)]
  
  sales<-df_final$sales
  scores<-c(training$y,testing$pred_ProphetScoresM)
  
  mod<-lm(sales~scores)
  #diff<-mod$fitted.values-sales
  training$pred_ProphetScoresM<-mod$fitted.values[1:(len-ntest)]
  testing$pred_ProphetScoresM<-mod$fitted.values[(len-ntest+1):len]
  
  c(rmse(sales[1:(len-ntest)],mod$fitted.values[1:(len-ntest)]))
  c(rmse(sales[(len-ntest+1):len],mod$fitted.values[(len-ntest+1):len]))
  
  model <- "ProphetScoresM"
  a <- c(rmse(sales[1:(len-ntest)],mod$fitted.values[1:(len-ntest)]),
         rmse(sales[(len-ntest+1):len],mod$fitted.values[(len-ntest+1):len]))
  b <- c(mape(sales[1:(len-ntest)],mod$fitted.values[1:(len-ntest)]),
         mape(sales[(len-ntest+1):len],mod$fitted.values[(len-ntest+1):len]))
  c <- c(prod,model,a,b)
  d_factorM[i, ] = c
  
  ## ------------------------------------------------------------------------
  
  ## Prophet with factor scores Rest
  AL$y.Rest<-df_final$Rest
  training$y<-AL$y.Rest[1:(len-ntest)]
  testing$y<-AL$y.Rest[(len-ntest+1):len]
  
  m_h_r <- prophet(holidays=s, mcmc_samples=300, 
                   holidays_prior_scale=0.5, 
                   changepoint_prior_scale=0.01, 
                   #seasonality_mode='multiplicative', 
                   yearly.seasonality=TRUE, 
                   #weekly.seasonality=TRUE, 
                   #daily.seasonality=FALSE
  )
  
  m_h_r <- add_regressor(m_h_r, 'promo_01')
  m_h_r <- add_regressor(m_h_r, "promo_02")
  m_h_r <- add_regressor(m_h_r, 'promo_03')
  m_h_r <- add_regressor(m_h_r, "promo_04")
  m_h_r <- add_regressor(m_h_r, 'promo_05')
  #m_h_r <- add_regressor(m_h_r, "pred.joghurt")
  #m_h_r <- add_regressor(m_h_r, "pred.gesund")
  #m_h_r <- add_regressor(m_h_r, "pred.joghurt.price")
  #m_h_r <- add_regressor(m_h_r, "pred.milk.price")
  m_h_r <- fit.prophet(m_h_r, training)
  
  future <- make_future_dataframe(m_h_r, periods = ntest, freq = "week", include_history = TRUE)
  
  future$promo_01<- AL[,c("promo_01")]
  future$promo_02<- AL[,c("promo_02")]
  future$promo_03<- AL[,c("promo_03")]
  future$promo_04<- AL[,c("promo_04")]
  future$promo_05<- AL[,c("promo_05")]
  #future$pred.joghurt<- AL[,c("pred.joghurt")]
  #future$pred.gesund<- AL[,c("pred.gesund")]
  #future$pred.joghurt.price<- AL[,c("pred.joghurt.price")]
  #future$pred.milk.price<- AL[,c("pred.milk.price")]
  
  fcst_h_r <- predict(m_h_r, future)
  
  n<-nrow(training)
  
  training$pred_ProphetScoresRest<-fcst_h_r$yhat[1:n]
  testing$pred_ProphetScoresRest<-fcst_h_r$yhat[(n+1):(n+ntest)]
  
  sales<-df_final$sales
  scores<-c(training$y,testing$pred_ProphetScoresRest)
  
  mod<-lm(sales~scores)
  diff<-mod$fitted.values-sales
  
  training$pred_ProphetScoresRest<-mod$fitted.values[1:(len-ntest)]
  testing$pred_ProphetScoresRest<-mod$fitted.values[(len-ntest+1):len]
  
  model <- "prophetScoresR"
  a <- c(rmse(sales[1:(len-ntest)],mod$fitted.values[1:(len-ntest)]),
         rmse(sales[(len-ntest+1):len],mod$fitted.values[(len-ntest+1):len]))
  b <- c(mape(sales[1:(len-ntest)],mod$fitted.values[1:(len-ntest)]),
         mape(sales[(len-ntest+1):len],mod$fitted.values[(len-ntest+1):len]))
  c <- c(prod,model,a,b)
  d_factorR[i, ] = c
  
  ## overwrite y from prophet to true sales again 
  
  training$y<-df_final$sales[1:(len-ntest)]
  testing$y<-df_final$sales[(len-ntest+1):len]
  
  ## store predicted data for plotting
  prediction[[i]]<-testing
  #print(c("All modells predicted for ", prod))
}
```

## Best models for each Yogurt

```{r evaluate}
library(hablar)
library(dplyr)
## create mape data frame of all models
## set correct data type (char to number)
y.m.df<-rbind(d_lm, d, d_glm, d_prop1, d_prop2, d_xgboost, d_factorM, d_factorR)%>% 
  retype()

## get best performing model for each yogurt
y.m.df %>%
  group_by(prod) %>%
  filter(mape_test == min(mape_test))
```



```{r}

```


## Plot predictions

```{r plot_sales, warning=FALSE}
library(ggplot2)

for(i in seq(1,length(prediction))){
  #i <-3
  
  yogurt <- dfs[[i]]$article_name[1]
  
  testing<-prediction[[i]]
  
  testqstat<- data.table::melt(prediction[[i]], id="ds", measure=c("pred_prophet1", 
                                                           "pred_prophet2", 
                                                           "pred_ProphetScoresM", 
                                                           "pred_xgboost"))
  model_names<- c(
    'pred_prophet1' = sprintf("basic Prophet\n MAPE: %.2f (Train) - %.2f (Test)",
                     mape(training$y, training$pred_prophet1),
                     mape(testing$y, testing$pred_prophet1)),
    
    'pred_prophet2' = sprintf("complex Prophet\n MAPE: %.2f (Train) - %.2f (Test)",
                     mape(training$y, training$pred_prophet2),
                     mape(testing$y, testing$pred_prophet2)),
    
    'pred_ProphetScoresM' = sprintf("M_scores Prophet \n  MAPE: %.2f (Train) - %.2f (Test)",
                     mape(training$y, training$pred_ProphetScoresM),
                     mape(testing$y, testing$pred_ProphetScoresM)),  
    
    'pred_xgboost' = sprintf("XGBoosting \n MAPE: %.2f (Train) - %.2f (Test)",
                     mape(training$y, training$pred_xgboost),
                     mape(testing$y, testing$pred_xgboost))
  )

  g1 <- ggplot(aes(y=value, x=ds, color=variable), data=testqstat) +
    
    xlim(min(testing$ds), max(testing$ds))+
    geom_line(data = testing, aes(y=y), color="grey70") +
    geom_line() +
    facet_wrap(~variable, ncol=2, labeller = as_labeller(model_names))+
    theme(axis.text = element_text(size=5), axis.title = element_text(size=6)) +
    labs(title=paste(c("Modelcomparison of ", yogurt, ", with MAPE Statistics."), collapse="",sep=""),  
         x="Time", y="Yogurt Sales")#+ 
    #theme(legend.position = "none")
  print(g1)
}
```

## Overview of best performing model

```{r model_overview}
## create data framewith all MAPE in testset
mape_test<-cbind(as.numeric(d_lm$mape_test),as.numeric(d_glm$mape_test),as.numeric(d$mape_test),as.numeric(d_prop1$mape_test),as.numeric(d_prop2$mape_test),as.numeric(d_xgboost$mape_test),as.numeric(d_factorM$mape_test),as.numeric(d_factorR$mape_test)) 

colnames(mape_test)<-c("lm","glm","tree","prop1","prop2","xgboost","factorM","factorR")
rownames(mape_test)<-d_glm[,1]

min<-apply(mape_test, 1, FUN = min)
a<-mape_test==min
colSums(a)
```